Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-17 ms.tex
referee comments

\newcommand{\Nfp}{6}
\newcommand{\Nvalidated}{18}
\newcommand{\Nlimbo}{12} %adds up to 36

@@

\begin{abstract}
The extended \kep\ mission, \KT, is now providing photometry of new fields every
three months in a search for transiting planets.
In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet
candidates orbiting 31 stars in \KT\ \Ci.
In this contribution, we present stellar and planetary properties for all systems.
We combine ground-based seeing-limited survey data and
adaptive optics imaging with an automated transit analysis scheme to validate
\Nvalidated\ candidates as planets
and identify \Nfp\ candidates as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \change{$2.24 \pm 0.25$ $R_\oplus$} planet with $T_{eq} = 271 \pm 16$ K and an
orbital period of 33 days.
We also present two new open-source software packages that enabled this analysis:
\texttt{isochrones}, a flexible tool for fitting theoretical stellar
models to observational data to determine stellar properties, and
\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
and statistically validate transiting exoplanets.
\end{abstract}

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties.
Additionally, there are no measured parallaxes for any of these stars.
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}.
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric all-sky survey (APASS) DR6
\citep{Henden14}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the $W1-W3$ WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit,
and in the remaining two cases, the photometric uncertainity in $W4$ is at least an
order of magnitude larger than those in $W1-W3$, so we do not use $W4$
for any system.
These data are reported in Table 1, and a color-color diagram showing the
$r-J, J-K$ colors of our candidates is included as Fig.~\ref{fig:photometry}.

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.
\change{We then run an MCMC chain using \texttt{MULTINEST} \citep{Feroz09},
an implementation of a multimodal nested sampling algorithm,}
for each host star conditioned on the observed
photometric properties as presented in Table 1.
We include a prior on stellar metallicity representative of the observed metallicities
of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
prior on mass (up to the maximum mass available in the model grids of $3.7$ $M_\odot$).

@@

@@

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new publicly available, general-purpose implementation
of the \citet{Morton12} procedure,
to calculate false positive probabilities (FPPs) for each of these
\KT\ candidates.
The following constraints on false positive
scenarios are imposed:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere inside
or within one pixel of the photometric aperture of the target star.
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out.
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail below).
\end{itemize}

@@

Table 4 summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 21 candidates
have FPP $<$ 1\%.
Two of these are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.
Four more of these 21 might plausibly be caused by
contamination by detected stellar companions within the photometric apertures
(see \S\ref{sec:background}), so we keep these as candidates.

This leaves 15 candidates that we statistically validate as planets, plus three
additional planets that \texttt{vespa} does not validate but have been previously
identified in the literature \citep{Crossfield15, Armstrong15b}.
So in total, of the 36 candidates, 18 are secure planets,
14 of which we here validate for the first time.

@@

@@

Images were registered and contrast curves were generated following \citet{Bowler15a}.
For the saturated data, the star's position in each image was found by masking the
saturated region and fitting a 2D bivariate Gaussian to the PSF wings.
Contrast
curves for the median-combined image are calibrated using the unsaturated frames.
The typical sensitivity is 6.5--7.5~mag at 1$''$.
The images were astrometrically calibrated using dithered observations of the
Trapezium cluster centered
on $\theta$$^1$~Ori~C taken on 2015 Feb 3 UT.
Based on the reference astrometry for pairs of stars in the field from
\citet{McCaughrean94}, we measure a plate scale of 25.2~$\pm$~0.4~mas pix$^{-1}$
and north orientation of --0.2~$\pm$~0.3$^{\circ}$.
Since this latter value is consistent with being aligned with
the detector columns, we adopt a value of 0.0~$\pm$~0.3$^{\circ}$ for this work.
Relative photometry of nearby stars is carried out using aperture photometry with
an aperture radius of 12~pix (0$\farcs$3).
For EPIC~201828749, we also acquired $J$- and $H$-band images.
Astrometry and photometry is derived separately for each image, and the mean and standard deviation
of these measurements is adopted for our final values listed in Table~5.

@@

Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distant background
stars is significantly lower.
We include all potential contaminants in Table 5.
We validate or eliminate each of these as a possibility based on the transit shape.
For example, the events near EPIC 201546283 could only be caused by a
background binary if the background object was a completely-eclipsing system
(so that the eclipse depth was $50\%$).
In this case, the transit would be perfectly V-shaped.
Since it is not, we can rule out the possibility this background object causes
the transit event.

In Table 5, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

The photometric apertures used to detect these candidates range in radius from
$10\farcs0$ to $19\farcs9$.  In order to be a plausible contaminant,
any companion star must
be either within this aperture or just outside but bright
enough for signficant flux to leak in.
Evaluating each of the systems listed in Table 5, we judge that we cannot yet
rule out contamination as a potential source of the transit signal for four
candidates: 201295312.01, 201403446.01, 201546283.01, and 201828749.01.
Despite receiving
low FPP scores from \texttt{vespa}, we list these systems as candidates in
Table 4, rather than planets.  Further updates to the \texttt{vespa} code
will allow consideration of ``specific'' false positive scenarios; that is,
scenarios that correspond to actually detected stars such as these, rather than
hypothetical background or bound companions.

@@

\subsection{Non-Astrophysical False Positives}
\label{sec:systematics}

@@

\acknowledgements
We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and
Jeff Coughlin (SETI) for
conversations and suggestions which improved the quality of this manuscript.
\change{We also thank Keivan Stassun (Vanderbilt) for his insights into 
extinction and stellar parameters in both \kep\ and \KT.
We thank the anonymous referee for their insightful comments as well.}

@@

@@

\begin{turnpage}
\include{table_planets}
\end{turnpage}
\include{table_fpp}

@@

>>>>

\newcommand{\Nfp}{7}
\newcommand{\Nvalidated}{20}
\newcommand{\Nlimbo}{9} %adds up to 36
\newcommand{\Nvalnew}{16} % 4 previously validated

@@

\begin{abstract}
The extended \kep\ mission, \KT, is now providing photometry of new fields every
three months in a search for transiting planets.
In a recent study, Foreman-Mackey and collaborators presented a list of 36 planet
candidates orbiting 31 stars in \KT\ \Ci.
In this contribution, we present stellar and planetary properties for all systems.
We combine ground-based seeing-limited survey data and
adaptive optics imaging with an automated transit analysis scheme to validate
\Nvalidated\ candidates as planets, \Nvalnew\ for the first time,
and identify \Nfp\ candidates as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \change{$2.24 \pm 0.25$ $R_\oplus$} planet with $T_{eq} = 271 \pm 16$ K and an
orbital period of 33 days.
We also present two new open-source software packages that enabled this analysis:
\texttt{isochrones}, a flexible tool for fitting theoretical stellar
models to observational data to determine stellar properties, and
\texttt{vespa}, a new general-purpose procedure to calculate false positive probabilities
and statistically validate transiting exoplanets.
\end{abstract}

@@

With the exception of one star in our sample (EPIC 201912552), we do not have
spectroscopic data with which to characterize the stellar properties.
Additionally, there are no measured parallaxes for any of these stars.
Instead, we rely on photometry.
For each system, we query the VizieR database of astronomical catalogues
\citep{Ochseinbein00}.
We record the $B$, $V$, $g'$, $r'$, and $i'$ magnitudes and their
uncertainties from the AAVSO Photometric All-Sky Survey (APASS) DR6
\citep{Henden14}, as reported in the UCAC4 Catalogue \citep{Zacharias12}.
We also record the $J$, $H$, and $K$ magnitudes and their uncertainties
as found in the 2MASS All-Sky Catalog of Point Sources \citep{Cutri03}
and the $W1-W3$ WISE magnitudes and uncertainties from the ALLWise Data
Release \citep{Cutri13}.
For all except two of our targets, the $W4$ band is only an upper limit,
and in the remaining two cases, the photometric uncertainity in $W4$ is at least an
order of magnitude larger than those in $W1-W3$, so we do not use $W4$
for any system.
These data are reported in Table 1, and a color-color diagram showing the
$r-J, J-K$ colors of our candidates is included as Fig.~\ref{fig:photometry}.

@@

In this work, we use grids from the Dartmouth Stellar
Evolution Database \citep{Dotter08} at solar values of \afe=$0.0$ and
helium abundance $Y=0.2741$, which come packaged with the \texttt{isochrones}
module.
\change{We then run an MCMC \btmtodo{still a chain?} using \texttt{MULTINEST} \citep{Feroz09},
an implementation of a multimodal nested sampling algorithm,}
for each host star conditioned on the observed
photometric properties as presented in Table 1.
We include a prior on stellar metallicity representative of the observed metallicities
of stars within 1 kpc of the Sun, following the results of \citet{Hayden15}, and a Salpeter-slope
prior on mass up to the maximum mass available in the model grids of $3.7$ $M_\odot$.

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
along that line of sight from the NED \btmtodo{acronym}, which reports the 
\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
COBE/DIRBE and IRAS/ISSA. 
The NED database returns the extinction in all relevant bandpasses except those used by
WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between 
SDSS, 2MASS, and WISE calculated by \citep{Davenport14}.
In each step of our fitting process, we draw an $A_V$, calculate the expected extinction
in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the 
observed apparent magnitudes.
We apply a uniform prior ranging from zero to the obtained maximum extinction value and
marginalize over extinction in our final determination of stellar parameters. }

@@

\change{\citet{Bastien14} use observations of stellar ``flicker'' to suggest that 
approximately 50 percent of planet host stars have evolved off the
main sequence onto the subgiant branch, so that both the host stars and their 
planets are larger than previously reported. 
Similarly, in \KT\ \Ci\ we may expect to find evolved stars in a sample of planet
candidates. 
Indeed, we find this to be the case.
Two stars, EPIC 201257461 and 201649426 are definitively evolved stars,
with derived radii in excess of 8 \rsun. For approximately one third of the others,
we find the stellar radius posterior distribution to be bimodal, with both main 
sequence and subgiant models of the stars being consistent with the photometric
data.
Future observations to measure the parallaxes of these stars, such as with Gaia,
will be helpful in differentiating between these two models to determine 
more precisely the stellar, and thus the planetary, radii.}

@@

In this work, we use
\texttt{vespa}\footnote{\url{http://github.com/timothydmorton/vespa}},
a new publicly available, general-purpose implementation
of the \citet{Morton12} procedure,
to calculate false positive probabilities (FPPs) for each of these
\KT\ candidates.
The following constraints on false positive
scenarios are imposed:
\begin{itemize}
\item A chance-aligned eclipsing binary system may reside anywhere inside
or within one pixel of the photometric aperture of the target star. 
\change{In creating a light curve for each star, we define photometric apertures ranging
from 10 to 20 arcseconds for each star, as defined in Table 4.
Given the 6-arcsecond PSF of the \kep\ telescope, we allow for the possibility
that companions falling just outside of our aperture (within one pixel) may
contribute to the light curve, possibly causing a false positive event.
The search for such companions is discussed in 
\textsection \ref{sec:background}.}
\item The maximum allowed depth of a potential secondary eclipse event
is the most significantly detected signal at the same
period of the planet candidate, once the primary transit is masked out 
(discussed in \textsection\ref{sec:sec}).
\change{\texttt{vespa} does not allow for the possibility of secondary eclipses 
larger than those observed in the \KT\ light curve for each star.}
\item Blended stars must be allowed by the available adaptive optics
and archival imaging data (discussed in detail in \textsection 
\ref{sec:AO} and \ref{sec:background}).
\change{\texttt{vespa} only considers stars below the detection threshold for
the AO imaging, which is a position-dependent value following a calculated
contrast curve for each star.}
\end{itemize}

@@

Table 5 summarizes the results of these
calculations, presenting the relative probability for each candidate
to be caused by any of three false positive scenarios: an undiluted
eclipsing binary (EB), a hierarchical triple eclipsing binary (HEB),
and a chance-aligned background(/foreground) eclipsing binary (BEB).

Four of the presented candidates have FPP $>$90\%;
these are considered to be likely false positives.
On the other hand, 23 candidates
have FPP $<$ 1\%.
Two of these are found to be caused by systematics
in the transit search noise model (details in \S\ref{sec:systematics}), and
so we identify those as false positives.
Four more of these 23 might plausibly be caused by
contamination by detected stellar companions within the photometric apertures
(see \S\ref{sec:background}), so we keep these as candidates.

This leaves 19 candidates that we statistically validate as planets, plus one
additional planets that \texttt{vespa} does not validate but have been previously
identified in the literature \citep{Crossfield15, Armstrong15b}.
So in total, of the 36 candidates, 20 are secure planets,
16 of which we here validate for the first time.

@@

\subsection{Secondary Eclipse Observations}
\label{sec:sec}
\change{One of the definitive signatures of a false positive binary star system masquerading
as a transiting planet is the presence of a secondary eclipse. While a nondetection of a secondary
does not exclude the possibility of a binary system (the orbit may be eccentric, 
or the companion too faint for a secondary eclipse to be detectable in the noise),
such a nondectection reduces the probability of each of the eclipsing binary false
positive scenarios.}

\change{To attempt to eliminate each eclipsing binary scenario, we first search each \KT\
light curve to determine which secondary eclipse signals are not allowed by the data.
We mask the transit signal of the planet in question and search for the most significant
signal at the same period. 
Such a scheme does not assume circular orbits: we return the most significant signal
at any phase, not only at the midpoint between consecutive transits.}

\change{We report these maximum allowable secondary eclipse depths in Table 5.
These values are used by \texttt{vespa} as limits on the allowable secondary eclipse.
Any models that cause a larger event, such as a background eclipsing binary 
consisting of two equal-mass stars in a circular orbit, can be excluded by the data.
We note that with the exception of EPIC 201505350.01, all systems with a maximum
eclipse depth of at least one part per thousand have FPPs of 0.866 or larger.
EPIC 201505350 is a two-planet system with the two planets near a 3:2 period
commensurability, so in this case the ``secondary'' is actually the transits of the 
other planet.}

@@

Images were registered and contrast curves were generated following \citet{Bowler15a}.
For the saturated data, the star's position in each image was found by masking the
saturated region and fitting a 2D bivariate Gaussian to the PSF wings.
Contrast
curves for the median-combined image are calibrated using the unsaturated frames.
The typical sensitivity is 6.5--7.5~mag at 1$''$.
The images were astrometrically calibrated using dithered observations of the
Trapezium cluster centered
on $\theta$$^1$~Ori~C taken on 2015 Feb 3 UT.
Based on the reference astrometry for pairs of stars in the field from
\citet{McCaughrean94}, we measure a plate scale of 25.2~$\pm$~0.4~mas pix$^{-1}$
and north orientation of --0.2~$\pm$~0.3$^{\circ}$.
Since this latter value is consistent with being aligned with
the detector columns, we adopt a value of 0.0~$\pm$~0.3$^{\circ}$ for this work.
Relative photometry of nearby stars is carried out using aperture photometry with
an aperture radius of 12~pix (0$\farcs$3).
For EPIC~201828749, we also acquired $J$- and $H$-band images.
Astrometry and photometry is derived separately for each image, and the mean and standard deviation
of these measurements is adopted for our final values listed in Table~4.

@@

Unlike the original \kep\ field, the field for \KT\ \Ci\ is
well out of the galactic plane, so the rate of giant, distant background
stars is significantly lower.
We include all potential contaminants in Table 4.
We validate or eliminate each of these as a possibility based on the transit shape.
For example, the events near EPIC 201546283 could only be caused by a
background binary if the background object was a completely-eclipsing system
(so that the eclipse depth was $50\%$).
In this case, the transit would be perfectly V-shaped.
Since it is not, we can rule out the possibility this background object causes
the transit event.

In Table 4, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

The photometric apertures used to detect these candidates range in radius from
$10\farcs0$ to $19\farcs9$.  In order to be a plausible contaminant,
any companion star must
be either within this aperture or just outside but bright
enough for signficant flux to leak in.
Evaluating each of the systems listed in Table 4, we judge that we cannot yet
rule out contamination as a potential source of the transit signal for four
candidates: 201295312.01, 201403446.01, 201546283.01, and 201828749.01.
Despite receiving
low FPP scores from \texttt{vespa}, we list these systems as candidates in
Table 5, rather than planets.  Further updates to the \texttt{vespa} code
will allow consideration of ``specific'' false positive scenarios; that is,
scenarios that correspond to actually detected stars such as these, rather than
hypothetical background or bound companions.

@@

\subsection{Other Sources of False Positives}
\label{sec:systematics}

@@

\acknowledgements
We thank Roberto Sanchis-Ojeda (Berkeley), Dan Huber (Sydney) and
Jeff Coughlin (SETI) for
conversations and suggestions which improved the quality of this manuscript.
\change{We also thank Keivan Stassun (Vanderbilt) for his insights into 
 stellar parameters for both \kep\ and \KT, which significantly improved
 this work.
We thank the anonymous referee for their insightful comments as well.}

@@

\btmtodo{NED?}

@@

\begin{turnpage}
\include{table_planets}
\end{turnpage}

@@

\include{table_fpp}
